% LaTeX Curriculum Vitae Template
%
% Copyright (C) 2004-2009 Jason Blevins <jrblevin@sdf.lonestar.org>
% http://jblevins.org/projects/cv-template/
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely. No attribution is
% required in any resulting documents. I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\documentclass[letterpaper]{article}

\usepackage{hyperref}
\usepackage{geometry}
\usepackage{etaremune}

% Comment the following lines to use the default Computer Modern font
% instead of the Palatino font provided by the mathpazo package.
% Remove the 'osf' bit if you don't like the old style figures.
\usepackage[T1]{fontenc}
\usepackage[sc,osf]{mathpazo}

% Set your name here
\def\name{Yangyang Xu}

% Replace this with a link to your CV if you like, or set it empty
% (as in \def\footerlink{}) to remove the link in the footer:
\def\footerlink{}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {economics, statistics, mathematics},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={6.5in, 8.5in},
  left=1.0in,
  top=1 in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name: Curriculum Vitae}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\scshape\large}
\subsectionfont{\rmfamily\mdseries\itshape\large}

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
  }
}{
  \end{list}
}

\begin{document}

% Place name at left
{\Large \name}

% Alternatively, print name centered and bold:
%\centerline{\Large \name}

\vspace{0.25in}

\begin{minipage}{0.99\linewidth}  
313B Gordon Palmer Hall   \\
\href{http://math.ua.edu}{Department of Mathematics}, \href{http://ua.edu/}{University of Alabama} \\
Box 870350, Tuscaloosa, AL 35487\\[0.2cm]
Email:  \href{mailto:yxu76@ua.edu}{\tt yxu76@ua.edu} \\
     Office Phone:  (+1)205-348-1975
\end{minipage}
%\begin{minipage}{0.45\linewidth}
  %\begin{tabular}{ll}
  
%Homepage: & \href{http://www.ima.umn.edu/~yangyang/}{\tt www.ima.umn.edu/$\sim$yangyang/} \\
    %Fax: &  (919) 962-5678 \\
    
  %\end{tabular}
%\end{minipage}
\hrule


\section*{Education}

\begin{minipage}{1\linewidth}
\begin{tabular}{ll}
\textbf{Rice University}, Houston, TX, USA. & \\
~~~~ Ph.D. in Computational and Applied Mathematics  &~~~~~~~~~~~~~~~~~~~~~~~~2014\\
~~~~ Thesis: ``Block coordinate update method in tensor optimization'' &\\
%~~~~ GPA: 4.09/4.30  & \\
~~~~ Advisor: Professor \href{http://www.math.ucla.edu/~wotaoyin/}{Wotao Yin} &\\[0.1cm]

\textbf{Chinese Academy of Sciences}, Beijing, China.\\
~~~~ M.S. in Operations Research &~~~~~~~~~~~~~~~~~~~~~~~~2010\\
~~~~ Thesis: ``On complexity of multi-task $n$-vehicle exploration problem.''& \\
%~~~~ GPA: 91/100& \\
~~~~ Advisor: Professor Jinchuan Cui &\\[0.1cm]

\textbf{Nanjing University}, Nanjing, China.& \\
~~~~ B.S. in Computational Mathematics  & ~~~~~~~~~~~~~~~~~~~~~~~~2007\\
%~~~~ GPA: 91/100, Ranking: 1/88 & \\
\end{tabular}
\end{minipage}

\section*{Employment}

%\subsection*{Rice University}
\begin{minipage}{1\linewidth}
\begin{tabular}{lc}
\textbf{University of Alabama, Tuscaloosa}&\\
~~~~ Assistant professor & Aug. 2016 --\\
\textbf{University of Minnesota, Twin Cities}&\\
~~~~ Postdoctoral fellow & \hfill Sep. 2015 -- Aug. 2016\\
~~~~ Mentor: Professor \href{http://www.menet.umn.edu/~zhangs/}{Shuzhong Zhang} &\\[0.1cm]
\textbf{University of Waterloo}&\\
~~~~ Postdoctoral fellow & \hfill Aug. 2014 -- Aug. 2015\\
~~~~ Advisors: Professors \href{http://www.math.uwaterloo.ca/~vavasis/}{Stephen Vavasis} and \href{http://www.math.uwaterloo.ca/~hwolkowi/}{Henry Wolkowicz} &\\[0.1cm]
%\textbf{Rice University} & \\
%~~~~ TA for CAAM 378: Introduction to Operations Research and Optimization & Fall 2013\\
%~~~~ TA for CAAM 335: Matrix Analysis & Spring 2013\\[0.1cm]
\textbf{Siemens Corporate Research} & \\
~~~~ {Intern}. Mentors: Drs. Ioannis  Akrotirianakis and Amit Chakraborty & Summer 2012 \\
 \hspace{0.5cm}Developed fast algorithms for binary and multi-class Support Vector Machines &\\
~~~~ with applications to microarray and texture classifications. & 

\end{tabular}
\end{minipage}

\section*{Research Interests}
%\subsection*{Current Focus}
\begin{itemize}\setlength{\itemsep}{-1pt}
\item Methodology: large-scale optimization, sparse optimization, stochastic computing, tensor optimization 
\item Applications: compressed sensing, image processing, machine learning, data mining
%\item low-rank matrix/tensor recovery, non-negative matrix/tensor factorization
\end{itemize}


\section*{Publication list}

\subsection*{Published or accepted}

%\begin{enumerate}\setlength{\itemsep}{-1.5pt}
\begin{etaremune}\setlength{\itemsep}{-1.5pt}
\item Z. Peng, T. Wu, \textbf{Y. Xu}, M. Yan and W. Yin. Coordinate Friendly Structures, Algorithms and applications. \emph{Annals of Mathematical Sciences and Applications}, 1(1), 57--119, 2016.
\item N. Zhou, \textbf{Y. Xu}, H. Cheng, J. Fang and W. Pedrycz. Global and local structure preserving sparse subspace learning: an iterative approach to unsupervised feature selection. \emph{Pattern Recognition}, 53, pp. 87--101, 2016.
\item \textbf{Y. Xu} and W. Yin. A fast patch-dictionary method for whole image recovery, \emph{Inverse problems and imaging}, 10(2), 2016.
\item \textbf{Y. Xu} and W. Yin. Block stochastic gradient iteration for convex and nonconvex optimization, \emph{SIAM Journal on Optimization}, 25(3), 1686--1716, 2015. \href{http://www.ima.umn.edu/~yangyang/papers/BSG.pdf}{[pdf]}
\item \textbf{Y. Xu}, R. Hao, W. Yin and Z. Su. Parallel matrix factorization for low-rank tensor completion, \emph{Inverse problems and imaging}, 9(2), 601--624, 2015. \href{http://aimsciences.org/journals/pdfs.jsp?paperID=10942&mode=full}{[pdf]}
\item \textbf{Y. Xu}. Alternating proximal gradient method for sparse nonnegative Tucker decomposition. \emph{Mathematical Programming Computation}, 7(1), 39--70, 2015. \href{http://link.springer.com/article/10.1007/s12532-014-0074-y}{[pdf]}
\item \textbf{Y. Xu}, I. Akrotirianakis and A. Chakraborty. Proximal gradient method for Huberized support vector machine, \emph{Pattern Analysis and Applications}, 2015. \href{http://link.springer.com/article/10.1007/s10044-015-0485-z}{[pdf]}
\item \textbf{Y. Xu}, I. Akrotirianakis and A. Chakraborty. Alternating direction method of multiplier for regularized multiclass support vector machines. \emph{Lecture Note in Computer Science}, 2015.
\item \textbf{Y. Xu}, W. Yin and S. Osher. Learning circulant sensing kernels. \emph{Inverse Problems and Imaging}, 8(3), 901--923, 2014. \href{http://www.aimsciences.org/journals/pdfs.jsp?paperID=10290&mode=full}{[pdf]}
\item \textbf{Y. Xu} and W. Yin. A block coordinate descent method for multi-convex optimization with applications to nonnegative tensor factorization and completion. \emph{SIAM Journal on Imaging Sciences}, 6(3), 1758--1789, 2013. \href{http://epubs.siam.org/doi/abs/10.1137/120887795}{[pdf]}
\item M. Lai, \textbf{Y. Xu} and W. Yin. Improved iteratively reweighted least squares for unconstrained smoothed $\ell_q$ minimization. \emph{SIAM Journal on Numerical Analysis}, 51(2), pp. 927--957, 2013.
\href{http://epubs.siam.org/doi/abs/10.1137/110840364}{[pdf]}
\item (Conference) Q. Ling, \textbf{Y. Xu}, W. Yin and Z. Wen. Decentralized low-rank matrix completion, {\em IEEE International Conference on Acoustics, Speech and Signal Processing} (ICASSP), pp. 2925--2928, 2012.
\href{http://ieeexplore.ieee.org/xpl/login.jsp?tp=&arnumber=6288528&url=http%3A%2F%2
Fieeexplore.ieee.org%2Fxpls%2Fabs_all.jsp%3Farnumber%3D6288528}{[pdf]}
\item \textbf{Y. Xu} and J. Cui. Multi-task $n$-vehicle exploration problem: complexity and algorithms. \emph{Journal of Systems Science and Complexity}, pp. 1080--1092, 2012.
%\item \textbf{Y. Xu} and J. Cui. A variant of multi-task $n$-vehicle exploration problem: maximizing every processor's average profit. {\em Acta Mathematicae Applicatae Sinica, English Series (Springer)}, 2012, pp. 463--474.
\item \textbf{Y. Xu}, W. Yin, Z. Wen and Y. Zhang. An alternating direction algorithm for matrix completion with nonnegative factors. {\em Journal of Frontiers of Mathematics in China, Special Issues on Computational Mathematics (Springer)}, 2011, pp. 365--384. \href{http://link.springer.com/article/10.1007/s11464-012-0194-5}{[pdf]}
\end{etaremune}
%\end{enumerate}

\subsection*{Under review}
\begin{enumerate}\setlength{\itemsep}{-1.5pt}
\item D. Oliveira, H. Wolkowicz and \textbf{Y. Xu}. ADMM for the SDP relaxation of the QAP. Submitted.
\item Z. Peng, \textbf{Y. Xu}, M. Yan and W. Yin. ARock: an algorithmic framework for asynchronous parallel coordinate updates. Submitted. \href{http://xxx.tau.ac.il/pdf/1506.02396v1.pdf}{[pdf]}
\item \textbf{Y. Xu}. On the convergence of higher-order orthogonality iteration. Submitted. \href{http://arxiv.org/pdf/1504.00538v1}{[pdf]}
\item \textbf{Y. Xu}. On higher-order singular value decomposition from incomplete data. Submitted.
\item \textbf{Y. Xu} and W. Yin. A globally convergent algorithm for nonconvex optimization based on block coordinate update. Submitted.
\href{ftp://ftp.math.ucla.edu/pub/camreport/cam13-38.pdf}{[pdf]}
\item J. Shi, \textbf{Y. Xu} and R. Baraniuk. Sparse bilinear logistic regression. Submitted.
\end{enumerate}

\section*{Computer Skills}
\begin{itemize}
\item MATLAB, C/C++, MPI, distributed/parallel computing, R, UNIX/Linux
\end{itemize}
~~~~\textbf{Software packages}
\begin{itemize}\setlength{\itemsep}{-1pt}
\item \href{http://www.math.ucla.edu/~wotaoyin/papers/tmac.html}{Tensor completion by parallel matrix factorization}
\item \href{http://www.math.ucla.edu/~wotaoyin/papers/bcu/}{Block-coordinate update for matrix and tensor factorization}
\item \href{http://www.caam.rice.edu/~optimization/circulant/}{Learning circulant kernels}
\end{itemize}


\section*{Invited talks}
\begin{itemize}
\setlength{\itemsep}{-0.5pt}
\item Block stochastic gradient update method. INFORMS Annual Meeting. Philadelphia, PA, Nov. 1--4, 2015.
\item On the convergence of higher-order orthogonality iteration and its extension. SIAM Conference on Applied Linear Algebra, Atlanta, GA, Oct. 26--30, 2015. 
\item Compressed higher-order singular value decomposition. \emph{AMMCS-CAIMS Congress}. Wilfrid Laurier University, Waterloo, Cananda, June 7--12, 2015
\item Low-rank tensor recovery via matrix factorization. \emph{SIAM Conference on CSE}. Salt Lake City, March 14--18, 2015.
\item Parallel matrix factorization for low-rank tensor completion. \emph{SIAM Conference on Optimization}. San Diego, CA, May 19--22, 2014.
\item Block coordinate descent in tensor optimization. \emph{Seminar of Department of Mathematics}, National University of Singapore, Feb. 10, 2014.
\item Block coordinate descent for multi-convex optimization. \emph{14th International Conference on Approximation Theory}. San Antonio, TX, April 7--10, 2013.
%\item Block coordinate descent for regularized multi-convex optimization, CAAM, Rice University, 10/31/2012.
\item Decentralized low-rank matrix completion, CAAM Colloquium, Rice University, Nov. 2, 2011.
\item Matrix completion with nonnegative factors, Math Colloquium, Shanghai Jiaotong University, Aug. 17, 2011.
\end{itemize}

\section*{Professional activities}
\textbf{Session Organizer}
\begin{itemize}\setlength{\itemsep}{-1.5pt}
\item SIAM Conference on Optimization, San Diego, CA, May 19--22, 2014
\item INFORMS Optimization Society Conference, Houston, TX, March 6--8, 2014
\end{itemize}
%\begin{minipage}{1\linewidth}
%\begin{tabular}{ll}
\textbf{Journal Referee} 
\begin{itemize}\setlength{\itemsep}{-1.5pt}
\item SIAM Journal on Imaging Sciences
\item SIAM Journal on Optimization 
\item SIAM Journal on Scientific Computing
\item Mathematical Programming
\item Applied Mathematics and Computation
\item Computational Optimization and Applications
\item Journal of Machine Learning Research
\item Journal of Computational Mathematics
\item Journal of Global Optimization
\item Journal of Mathematical Imaging and Vision
\item Journal of Operations Research Society of China
\item Journal of Optimization Theory and Application
\item Journal of Scientific Computing 
\item IEEE Signal Processing
\item IEEE Neural Network and Learning System
%\end{tabular}
\end{itemize}
%\end{minipage}


\section*{Honors and Awards}
\begin{itemize}\setlength{\itemsep}{-1.5pt}
\item Alan Weiser Memorial Travel Award, Rice University \hfill 2014
\item Graduate fellowship, {Rice University} \hfill 2010 -- 2011
\item Championship of the Enterprise Simulation Contest of {Chinese Academy of Sciences} \hfill 2008
\item First Prize, Scholarship  of {Nanjing University} \hfill 2006
\item First Prize, National Scholarship of China \hfill 2005
\item Samsung Scholarship \hfill 2004

\end{itemize}

%\section*{References}
%\begin{minipage}{1\linewidth}
%\begin{tabular}{ll}
%\textbf{Wotao Yin} & Ph.D advisor\\
%& Professor of Mathematics, UCLA\\
%&  \href{mailto: wotaoyin@math.ucla.edu}{\tt wotaoyin@math.ucla.edu}\\[0.1cm]
%\textbf{Stanley Osher} & Professor of Mathematics, UCLA\\
%& \href{mailto: sjo@math.ucla.edu}{\tt sjo@math.ucla.edu}\\[0.1cm]
%\textbf{Yin Zhang} & Professor of Computational and Applied Mathematics, Rice University\\
%& \href{mailto: yzhang@rice.edu}{\tt yzhang@rice.edu}\\[0.1cm]
%\textbf{Richard Tapia} & Professor of Computational and Applied Mathematics, Rice University\\
%& \href{mailto: rat@rice.edu}{\tt rat@rice.edu}
%\end{tabular}
%\end{minipage}

\bigskip

\end{document}
